% A&A structured abstract
% Context / Aims / Methods / Results / Conclusions

\context{
Wolf-Rayet (WR) stars of the carbon sequence (WC/WO) represent the final
stripped stages of massive stellar evolution, yet the role of binary
interactions in their formation remains debated. The Large Magellanic Cloud
(LMC), at $Z \approx 0.3$--$0.5\,\Zsun$, provides a critical low-metallicity
environment to test theoretical predictions of the WR binary fraction.
}

\aims{
We aim to determine the spectroscopic binary fraction of LMC WC/WO stars
and constrain the intrinsic binary fraction and orbital period distribution
through Monte-Carlo bias correction.
}

\methods{
We analyse multi-epoch VLT/X-SHOOTER spectroscopy of \Nstars apparently
single WC/WO stars in the LMC across \Nepochs epochs. Radial velocities are
measured via cross-correlation of the \primaryline emission line. Binary
classification requires $\Delta\mathrm{RV} > \drvthresh$\,\kms and a
$\sigthresh\sigma$ significance threshold. The intrinsic binary fraction and
period-distribution exponent are constrained by comparing the observed
$\Delta\mathrm{RV}$ distribution to Monte-Carlo simulations via a
Kolmogorov--Smirnov test.
}

\results{
We detect \Ndetected new spectroscopic binaries, yielding a total of
$\Nbin/\Ntotal = \fbinobs$ when combined with \Nknown previously known
binaries. The bias-corrected intrinsic binary fraction is
$f_\mathrm{bin} = \fbincorr^{+\fbinerrup}_{-\fbinerrdn}$, with a
period-distribution exponent $\pi = \pibestfit^{+\pierrup}_{-\pierrdn}$.
}

\conclusions{
% TODO: Fill in after bias correction errors are finalized.
}
