\section{Bias correction}
\label{sec:bias}

The observed binary fraction is a lower limit on the true binary fraction,
since spectroscopic surveys are biased against detecting systems with long
orbital periods, low inclinations, or low mass ratios. Following the
methodology of \citet{Dsilva2023}, we employ a Monte-Carlo simulation to
constrain the intrinsic binary fraction $f_\mathrm{bin}$ and the
orbital-period distribution exponent $\pi$.

\subsection{Simulation framework}
\label{sec:sim_framework}

For each point on a two-dimensional grid in $(f_\mathrm{bin}, \pi)$, we
generate \Nsim synthetic stellar systems as follows:

\begin{enumerate}
\item Each system is assigned as binary with probability $f_\mathrm{bin}$,
  or single otherwise.

\item For binary systems, orbital parameters are drawn from the following
  distributions:
  \begin{itemize}
  \item \textbf{Period:} $p(\log P) \propto (\log P)^{\pi}$, with
    $\log P \in [0.15, 5.0]$\,days.
  \item \textbf{Eccentricity:} uniform on $[0, e_\mathrm{max}]$ with
    $e_\mathrm{max} = 0.9$.
  \item \textbf{Mass ratio:} $q = M_2/M_1$ uniform on $[0.1, 2.0]$.
  \item \textbf{Inclination:} $p(i) \propto \sin i$, $i \in [0, \pi/2]$
    (isotropic orientations).
  \item \textbf{Primary mass:} $M_1 = 10$\,\Msun (fixed) or drawn
    uniformly from $[10, 20]$\,\Msun.
  \end{itemize}

\item The radial-velocity semi-amplitude $K_1$ is computed from Kepler's
  third law:
  \begin{equation}
  K_1 = \left(\frac{2\pi G}{P}\right)^{1/3}
        \frac{M_2 \sin i}{(M_1 + M_2)^{2/3}}
        \frac{1}{\sqrt{1 - e^2}}.
  \label{eq:K1}
  \end{equation}

\item Radial-velocity curves are generated by solving Kepler's equation
  numerically, sampling at the actual observation epochs (MJD timestamps)
  of the \Nstars target stars.

\item Observational noise is added: $\sigma_\mathrm{single} =
  \sigmasingle$\,\kms (intrinsic wind variability for single stars) and
  $\sigma_\mathrm{meas} = \sigmameas$\,\kms (per-epoch measurement
  uncertainty).
\end{enumerate}

\subsection{Comparison to observations}
\label{sec:ks_test}

For each grid point, we compute the peak-to-peak
$\Delta\mathrm{RV}_\mathrm{max}$ of each simulated star and construct the
cumulative distribution function (CDF) of $\Delta\mathrm{RV}$ values. This
simulated CDF is compared to the observed CDF using a two-sample
Kolmogorov--Smirnov (K-S) test. The best-fit model is the grid point that
minimises the K-S statistic $D$ (equivalently, maximises the $p$-value).

\subsection{Grid search and results}
\label{sec:grid_results}

The grid spans $f_\mathrm{bin} \in [0.3, 1.0]$ with step 0.005--0.01, and
$\pi \in [-3, +1]$. The search is parallelised across
$N_\mathrm{cores} - 1$ CPU cores.

% TODO: Insert heatmap figure showing K-S D statistic over (f_bin, pi).
% TODO: Insert CDF comparison at best-fit point.
% TODO: Report best-fit values with errors from marginalized posteriors.

The best-fit parameters are $f_\mathrm{bin} =
\fbincorr^{+\fbinerrup}_{-\fbinerrdn}$ and $\pi =
\pibestfit^{+\pierrup}_{-\pierrdn}$, where the uncertainties represent
68\% highest-density intervals from the marginalised K-S $p$-value
distribution.

\subsection{Alternative period distribution: Langer+2020}
\label{sec:langer_model}

As a consistency check, we also consider the theoretically motivated
period distribution of \citet{Langer2020}, derived from binary population
synthesis of OB+black hole systems using MESA. Unlike the empirical
power-law model of Sect.~\ref{sec:sim_framework}, this distribution is
physically motivated by the two dominant mass-transfer channels that
produce post-interaction binaries.

The period distribution is modelled as a two-component mixture:
\begin{equation}
p(\log P) = w_\mathrm{A}\,\mathcal{N}(\log P \mid \mu_\mathrm{A},
\sigma_\mathrm{A}) + (1 - w_\mathrm{A})\,
\mathrm{LogNorm}(\log P \mid \mu_\mathrm{B}, \sigma_\mathrm{B}),
\label{eq:langer_period}
\end{equation}
where:
\begin{itemize}
\item \textbf{Case~A} (short-period Roche-lobe overflow): a Gaussian in
  $\log P$ with $\mu_\mathrm{A} = 0.80$ and $\sigma_\mathrm{A} = 0.15$,
  corresponding to orbital periods of $\sim$\,3--10\,days;
\item \textbf{Case~B} (wide-orbit mass transfer): a log-normal
  distribution in $\log P$ space with mode $\mu_\mathrm{B} = 2.0$ and
  shape parameter $\sigma_\mathrm{B} = 0.2$, producing a right-skewed
  tail toward longer periods ($P \sim 30$--3000\,days), as seen in
  Fig.~6 of \citet{Langer2020};
\item $w_\mathrm{A} = 0.2$, reflecting the theoretical prediction that
  Case~B dominates (${\sim}\,80$\% of post-interaction systems).
\end{itemize}

The remaining orbital parameters differ from the power-law model in two
respects. First, all orbits are assumed circular ($e = 0$), appropriate
for post-Roche-lobe-overflow systems whose orbits have been tidally
circularised. Second, the mass ratio follows a Gaussian distribution
$q \sim \mathcal{N}(0.7, 0.2)$, clipped to $[0.25, 1.75]$, motivated
by the BH mass distribution in Fig.~4 of \citet{Langer2020} where
$M_\mathrm{BH}/M_\mathrm{OB}$ peaks at ${\sim}\,0.5$--$0.7$.

With the period distribution fixed by theory, the grid search reduces to
a two-dimensional scan over $(f_\mathrm{bin},\,\sigma_\mathrm{single})$,
where $\sigma_\mathrm{single}$ is the intrinsic single-star RV scatter
(treated as a nuisance parameter). The same K-S comparison methodology
(Sect.~\ref{sec:ks_test}) is applied.

% TODO: Report best-fit f_bin from Langer model with HDI68 errors.
% TODO: Compare Langer vs Dsilva corrected binary fractions.
% TODO: Insert figure showing Langer K-S heatmap over (f_bin, sigma_single).
