\section{Radial-velocity measurement and binary classification}
\label{sec:methods}

\subsection{Cross-correlation function}
\label{sec:ccf}

Radial velocities were measured using the one-dimensional
cross-correlation function (CCF) technique of \citet{Zucker1994}. For each
star, a high signal-to-noise template spectrum was constructed by first
computing the CCF of all epochs against an arbitrary reference epoch to
determine relative velocity shifts, correcting each epoch to a common rest
frame, and then co-adding the corrected spectra with signal-to-noise
squared weighting. This iterative procedure removes the dependence on the
choice of reference epoch.

The CCF was computed separately for each of the 11 emission lines listed
in Table~\ref{tab:emission_lines}, spanning the full X-SHOOTER wavelength
range from the ultraviolet (\ion{O}{v}\,$\lambda\lambda 3100$--$3175$) to
the near-infrared (\ion{C}{iv}\,$\lambda 20842$). The radial velocity for
each epoch was determined from the position of the CCF peak, and its
formal uncertainty $\sigma_\mathrm{RV}$ from the curvature of the peak
\citep{Zucker2003}.

% Emission line table
\begin{table}
\caption{Emission lines used for cross-correlation analysis.}
\label{tab:emission_lines}
\centering
\begin{tabular}{lcc}
\hline\hline
Line ID & $\lambda_\mathrm{min}$ [nm] & $\lambda_\mathrm{max}$ [nm] \\
\hline
\ion{O}{v}\,$\lambda\lambda 3100$--$3175$   & 310.0 & 317.5 \\
\ion{O}{iv}\,$\lambda\lambda 3350$--$3480$  & 335.0 & 348.0 \\
\ion{C}{iv}\,$\lambda\lambda 3650$--$3900$  & 365.0 & 390.0 \\
\ion{He}{ii}\,$\lambda 4686$                & 456.0 & 480.0 \\
\ion{O}{vi}\,$\lambda\lambda 5210$--$5340$  & 521.0 & 533.5 \\
\ion{He}{ii}\,$\lambda 5412$ \& \ion{C}{iv}\,$\lambda 5471$ & 535.0 & 554.0 \\
\ion{C}{iv}\,$\lambda\lambda 5808$--$5812$  & 570.0 & 588.0 \\
\ion{C}{iii}\,$\lambda\lambda 6700$--$6800$ & 666.5 & 684.0 \\
\ion{C}{iv}\,$\lambda 7063$                 & 697.0 & 714.0 \\
\ion{C}{iv}\,$\lambda 17396$                & 1710.0 & 1763.0 \\
\ion{C}{iv}\,$\lambda 20842$                & 2050.0 & 2100.0 \\
\hline
\end{tabular}
\end{table}

\subsection{Binary classification criteria}
\label{sec:criteria}

A star is classified as a spectroscopic binary if \emph{both} of the
following criteria are satisfied \citep[following][]{Bartzakos2001,
Dsilva2023}:

\begin{enumerate}
\item The peak-to-peak radial-velocity difference between any pair of
  epochs exceeds $\Delta\mathrm{RV}_\mathrm{max} > \drvthresh$\,\kms.
\item The detection is statistically significant:
  $\Delta\mathrm{RV} - \sigthresh\sigma > 0$, where
  $\sigma = \sqrt{\sigma_1^2 + \sigma_2^2}$ is the combined formal
  uncertainty of the epoch pair.
\end{enumerate}

The classification is performed in two stages. First, the epoch pair with
the maximum radial-velocity separation is evaluated. If this pair does not
satisfy both criteria, all remaining epoch pairs are scanned. The binary
decision is based exclusively on the \primaryline emission line, the
strongest and most isolated WC spectral feature.

\subsection{Signal-to-noise requirements}
\label{sec:snr}

To ensure reliable radial-velocity measurements, we established minimum
signal-to-noise requirements per emission line through simulations. We
generated 30 synthetic single-lined binary (SB1) spectra using a WC4
template with varying S/N levels, measured the radial-velocity scatter for
each line, and required $\sigma_\mathrm{RV} < 3$\,\kms as the acceptance
threshold.
