\section{Sample and observations}
\label{sec:obs}

\subsection{Target sample}
\label{sec:sample}

Our sample consists of \Ntotal WC- and WO-type Wolf-Rayet stars in the
Large Magellanic Cloud, drawn from the catalogue of
\citet{Breysacher1999} and the survey of \citet{Bartzakos2001}. Of these,
\Nknown were previously identified as spectroscopic binaries by
\citet{Bartzakos2001}; the remaining \Nstars stars were classified as
apparently single and form the primary targets of our survey.
Table~\ref{tab:sample} lists the target stars with their designations,
spectral types, and number of observed epochs.

% TODO: Add table reference once star_sample.tex is populated.

\subsection{VLT/X-SHOOTER spectroscopy}
\label{sec:xshooter}

Multi-epoch spectroscopy was obtained with the X-SHOOTER spectrograph
\citep{Vernet2011} mounted on the ESO Very Large Telescope (VLT) at Cerro
Paranal, Chile. X-SHOOTER provides simultaneous coverage across three
spectral arms: UVB ($\sim 300$--$560$\,nm), VIS ($\sim 560$--$1020$\,nm),
and NIR ($\sim 1020$--$2480$\,nm), at intermediate spectral resolution
($R \sim 10\,000$). Each target was observed in \Nepochs epochs spanning
three semesters, aiming for a signal-to-noise ratio $\mathrm{S/N} \geq 70$
per epoch.

% TODO: Add ESO programme ID and observation dates.

\subsection{Data reduction}
\label{sec:reduction}

The raw data were reduced using the ESO X-SHOOTER pipeline, producing
wavelength-calibrated, flux-calibrated one-dimensional spectra for each
arm. We describe the subsequent post-processing steps below.

\subsubsection{Spectral combination}
\label{sec:stitching}

The three spectral arms were combined into a single spectrum per epoch
using signal-to-noise-squared weighting. In the overlap regions between
adjacent arms, we computed the mean flux in the last $5\%$ of the overlap
for the redder arm and the corresponding region of the bluer arm, deriving
an alignment factor $A = \bar{F}_\mathrm{red} / \bar{F}_\mathrm{blue}$.
The spectra were considered consistent if
\begin{equation}
|\bar{F}_\mathrm{red} - \bar{F}_\mathrm{blue}| <
\frac{\sqrt{\sigma_\mathrm{red}^2 + \sigma_\mathrm{blue}^2}}{\sqrt{N}}.
\end{equation}
Where the spectral sampling differed (e.g.\ NIR at 0.04\,nm vs.\ VIS at
0.02\,nm), the lower-resolution spectrum was linearly interpolated to the
finer grid before combination. The combined flux was computed as
$F_\mathrm{comb} = \sum w_i f_i$ with weights
$w_i = \mathrm{SNR}_i^2 / \sum \mathrm{SNR}_i^2$.

\subsubsection{Continuum normalisation}
\label{sec:normalisation}

Continuum normalisation was performed interactively using a custom tool.
Anchor points were placed on featureless continuum regions (avoiding
emission and absorption lines). The flux at each anchor point was computed
as the robust mean (iterative $3\sigma$ clipping) of the flux in a narrow
window. A piecewise linear interpolation between anchor points defined the
pseudo-continuum, and the observed spectrum was divided by this
interpolation. The same anchor wavelengths were used for all epochs of a
given star to ensure consistency.

\subsubsection{Spatial contamination removal}
\label{sec:contamination}

% TODO: Describe 2D cleaning procedure from IC2D.py.
For stars with significant contamination from nearby sources in the slit,
we examined the two-dimensional spectral images to identify and subtract
the contaminating spatial profile before extracting the cleaned
one-dimensional spectrum.
